Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-18 paper/main.tex
xi

\begin{definition} A category \mathcal{C} consists of a collection of objects $C$ with identity $id_c: C\rightarrow C$ and the set of morphisms between every two objects $f:C_1 \rightarrow C_2$, \cite{fongInvitationAppliedCategory2019,maclaneCategoriesWorkingMathematician2013}. 
\end{definition}
The set of morphisms between objects is termed the hom set $hom_{\mathcal{C}}(C_1, C_2)$. The morphisms on the category  compose
\begin{equation*}
  \begin{tikzcd}
    C_1 \arrow[r, "f"] \arrow[rd, "g\circ f"'] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145] & C_2 \arrow[d, "g"] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55] \\
  & C_3 \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235]              
  \end{tikzcd}
\end{equation*}
 and are constructed such that the following axioms hold \cite{riehlCategoryTheoryContext}:
 \begin{LaTeXdescription}
   \item[associativity] if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
   \item[identity] for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
 \end{LaTeXdescription}

@@

 \begin{definition} A functor is a morphism between categories $\mathfrak{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}
A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. Contravariant functors are functors where the morphisms in $\mathcal{C}$ go in the opposite direction from the morphisms in $\mathcal{D}$.

@@

\begin{definition} \label{def:category:K} The category of open sets $\mathcal{\dbasec}$ consists of
  \begin{itemize}
    \item \textit{objects} open sets $\openset_{j} \in \{openset\}$ in the topological space $(\dbase, \mathscr{T})$), including the empty set $\varnothing$ and the maximum set \dbase. 
    \item \textit{morphisms} $\iota: U_{j} \hookrightarrow U_{k}$ for all  $U_j, U_k \subset \dtotal$
  \end{itemize} 
\end{definition}

>>>>

\begin{definition} A category \mathcal{C} consists of a collection of objects $c$ with identity $id_c: C\rightarrow C$ and the set of morphisms between every two objects $f:C_1 \rightarrow C_2$, \cite{fongInvitationAppliedCategory2019,maclaneCategoriesWorkingMathematician2013}. 
\end{definition}
The set of morphisms between objects is termed the hom set $hom_{\mathcal{C}}(C_1, C_2)$. The morphisms on the category  compose
\begin{equation*}
  \begin{tikzcd}
    C_1 \arrow[r, "f"] \arrow[rd, "g\circ f"'] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145] & C_2 \arrow[d, "g"] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55] \\
  & C_3 \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235]              
  \end{tikzcd}
\end{equation*}
 and are constructed such that the following axioms hold \cite{riehlCategoryTheoryContext}:
 \begin{LaTeXdescription}
   \item[associativity] if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
   \item[identity] for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
 \end{LaTeXdescription}

@@

 \begin{definition} A functor is a morphism between any two  categories $\mathfrak{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}
A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. Contravariant functors are functors where the morphisms in $\mathcal{C}$ go in the opposite direction from the morphisms in $\mathcal{D}$.

@@

\begin{definition} \label{def:category:K} The category of open sets $\mathcal{\dbasec}$ consists of
  \begin{itemize}
    \item \textit{objects} open sets $\openset_{i} \in \{openset\}$ in the topological space $(\dbase, \mathscr{T})$), including the empty set $\varnothing$ and the maximum set \dbase. 
    \item \textit{morphisms} $\iota: \openset_{i} \hookrightarrow \openset_{j}$ for all  $\openset_i, \openset_j \subset \dtotal$
  \end{itemize} 
\end{definition}

We also introduce a category of open sets called $\mathcal{\gbase}$ that encapsulates the topology of the graphic display space. The category $\mathcal{\gtotal}$ has  inclusion morphisms $\iota: {\openset_{i}}^{\prime} \hookrightarrow {\openset_{j}}^{\prime}$, including into the total set \gtotal. We introduce a surject map $\vindex: \gtotal \rightarrow \dtotal$ from the the graphic base space to the data base space. Given the morphism $\iota$
\begin{equation}
  \label{eq:artist:vindex}
  \begin{tikzcd}
    & \opensetc^{\prime}_i \arrow[d, "\iota"] \\
  \dbasec \arrow[ru, "\vindexc^*", dashed] & \gbasec \arrow[l, "\vindexc"]   
\end{tikzcd}
\end{equation}
we propose that the map \vindex\ can be pulled back to a map between open sets in \dbase and open sets in \gbase. This map is the functor
\begin{equation}
  \vindex^{*}:\mathcal{\dtotal} \rightarrow \mathcal{\gtotal}
\end{equation}
that maps from the data base space to the graphic base space. The map $\vindex^{*}$ is a lookup map between where a point is located in the data and where it is located on screen.
